>

### 2020-03-16 manuscript/manuscript.Rmd
Clean up adding appendix to end of paper
This brings in the appendix as a tex document instead of a markdown document. The tex document
needs to be edited to remove its tex preamble and final end{document} but it seems to work ok.

---
title: >
  Modeling the impacts of park access on health outcomes: a utility-based 
  accessibility approach
runninghead: Macfarlane \emph{et al}.
author:
  - name: Gregory Macfarlane
    num: 1
  - name: Nico Boyd
    num: 2
  - name: John E. Taylor
    num: 3
  - name: Kari Watkins
    num: 3
address:
  - code: 1
    address: Civil and Environmental Engineering Department, Brigham Young University 
  - code: 2
    address: Fehr and Peers, Los Angeles, California
  - code: 3
    address: School of Civil and Environmental Engineering, Georgia Institute of Technology
corrauth: "Gregory Macfarlane, 430 Engineering Building, Provo UT 84663"
email: gregmacfarlane@gmail.com
abstract: >
  Recent research has underscored the potential for public green spaces to influence individual and societal health outcomes, but empirical measurements of such influences have yielded mixed results to date, with particular disagreement surrounding how access to parks ought to be defined while controlling for alternate explanations. In this paper we apply a comprehensive measure of park accessibility drawn from random utility choice theory, which avoids arbitrary assertions of proximity while incorporating potentially numerous amenities and attributes of both the parks and the population. We apply this utility-based accessibility measure to correlate Census tract-level obesity and physical activity rate estimates from the Centers for Disease Control and Prevention's 500 Cities project with tract-level American Community Survey socioeconomic data in New York City, paired with geographic open space data from New York City. Controlling for the socioeconomic variables and spatially correlated error terms, we show a positive and significant relationship between park access and physical activity rates. The data also suggest a negative relationship between park access and obesity rates, beyond what is expected through physical activity and socioeconomics. In doing so, this research contributes a more comprehensive modeling approach for measuring the impact of park access on health, and may improve our understanding of the role  parks and access to them can serve in furthering public health objectives.
keywords: Accessibility; Green Space
classoption:
  - shortAfour
output: 
  rticles::sage_article:
    keep_md: yes
    keep_tex: yes
    includes: 
      in_header: preamble.tex
      after_body: appendix.md
bibliography: library.bib
bibliographystyle: sageh.bst
---

>>>>

---
title: >
  Modeling the impacts of park access on health outcomes: a utility-based 
  accessibility approach
runninghead: Macfarlane \emph{et al}.
author:
  - name: Gregory Macfarlane
    num: 1
  - name: Nico Boyd
    num: 2
  - name: John E. Taylor
    num: 3
  - name: Kari Watkins
    num: 3
address:
  - code: 1
    address: Civil and Environmental Engineering Department, Brigham Young University 
  - code: 2
    address: Fehr and Peers, Los Angeles, California
  - code: 3
    address: School of Civil and Environmental Engineering, Georgia Institute of Technology
corrauth: "Gregory Macfarlane, 430 Engineering Building, Provo UT 84663"
email: gregmacfarlane@gmail.com
abstract: >
  Recent research has underscored the potential for public green spaces to influence individual and societal health outcomes, but empirical measurements of such influences have yielded mixed results to date, with particular disagreement surrounding how access to parks ought to be defined while controlling for alternate explanations. In this paper we apply a comprehensive measure of park accessibility drawn from random utility choice theory, which avoids arbitrary assertions of proximity while incorporating potentially numerous amenities and attributes of both the parks and the population. We apply this utility-based accessibility measure to correlate Census tract-level obesity and physical activity rate estimates from the Centers for Disease Control and Prevention's 500 Cities project with tract-level American Community Survey socioeconomic data in New York City, paired with geographic open space data from New York City. Controlling for the socioeconomic variables and spatially correlated error terms, we show a positive and significant relationship between park access and physical activity rates. The data also suggest a negative relationship between park access and obesity rates, beyond what is expected through physical activity and socioeconomics. In doing so, this research contributes a more comprehensive modeling approach for measuring the impact of park access on health, and may improve our understanding of the role  parks and access to them can serve in furthering public health objectives.
keywords: Accessibility; Green Space
classoption:
  - shortAfour
output: 
  rticles::sage_article:
    keep_md: yes
    keep_tex: yes
    includes: 
      in_header: preamble.tex
      after_body: appendix.tex
bibliography: library.bib
bibliographystyle: sageh.bst
---
